\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-27 introduction.tex
soften claim in intro

\item We present, to our knowledge, the first\EDJ{Are you sure? This claim is so bold.}\YZreply{Is there any previous language designs in this space?} language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the rigor of a proof assistant,
while retaining an idiomatic programming style.

>>>>

\item We present a
%\EDJ{Are you sure? This claim is so bold.}\YZreply{Is there any previous language designs in this space?}\EDJreply{Olivier Boite. 2004. Proof reuse with extended inductive types. In International Conference on Theorem Proving in
%Higher Order Logics. Springer, 50–65.  I think I also mentioned several paper in the related work.}
language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the rigor of a proof assistant,
while retaining an idiomatic programming style.
